\mytitle

### 2020-04-22 paper.tex
Spell check

\paragraph{Wakes}
Turbines influence each other through \emph{wake} interference effects~\cite{jensen1983note,shakoor2016wake}.
%that are
%referred to as \emph{wakes}~\cite{jensen1983note,shakoor2016wake}.
Wakes cause reduction of the effective power produced by a turbine due
to upstream turbines that change the airflow dynamics. In
Figure~\ref{fig:field_model}, the wind is assumed to be
blowing from left to right. The wake effect due to placing the turbine
expands as shown in the diagram.
%: it will influence only turbines that
%are placed in the orange cells.  In other words,
If a turbine is placed in the orange area, its effective power is
reduced due to the upstream turbine.
% that we placed in the $8\times8$ farm.
Moreover, a given turbine may be placed downstream from multiple turbines and hence
multiple wakes must be taken into account for each location.  The
reduction of power due to the wake effect is determined by three
parameters: (1) the distance between the upstream turbine and the cell
for which we want to compute the effect (denoted by $x$ in
Figure~\ref{fig:field_model}), (2) the radius of the cone's opening at distance $x$ 
(denoted by $r$ in Figure~\ref{fig:field_model}), and (3) the
combination of several wind regimes where a wind regime consists of 
ther wind's free speed and direction.  The wake effect can be pre-computed
for each pair of cells since we know: the distance ($x$), the turbine
specifications and terrain conditions (that jointly dictate $r$), and
probabilistic behavior of wind regimes~\cite{Zhang2014}.

>>>>

\paragraph{Wakes}
Turbines influence each other through \emph{wake} interference effects~\cite{jensen1983note,shakoor2016wake}.
%that are
%referred to as \emph{wakes}~\cite{jensen1983note,shakoor2016wake}.
Wakes cause reduction of the effective power produced by a turbine due
to upstream turbines that change the airflow dynamics. In
Figure~\ref{fig:field_model}, the wind is assumed to be
blowing from left to right. The wake effect due to placing the turbine
expands as shown in the diagram.
%: it will influence only turbines that
%are placed in the orange cells.  In other words,
If a turbine is placed in the orange area, its effective power is
reduced due to the upstream turbine.
% that we placed in the $8\times8$ farm.
Moreover, a given turbine may be placed downstream from multiple turbines and hence
multiple wakes must be taken into account for each location.  The
reduction of power due to the wake effect is determined by three
parameters: (1) the distance between the upstream turbine and the cell
for which we want to compute the effect (denoted by $x$ in
Figure~\ref{fig:field_model}), (2) the radius of the cone's opening at distance $x$ 
(denoted by $r$ in Figure~\ref{fig:field_model}), and (3) the
combination of several wind regimes where a wind regime consists of 
the wind's free speed and direction.  The wake effect can be pre-computed
for each pair of cells since we know: the distance ($x$), the turbine
specifications and terrain conditions (that jointly dictate $r$), and
probabilistic behavior of wind regimes~\cite{Zhang2014}.
